Checkpoint 4

### 2020-05-01 Draft-Report.Rmd
cleaning

```{r}
set.seed(454)
model_1 <- stan_glm(
  ChinaVirusInterest ~ Day + percent_white+StateColor+positive,
  data = model_data, family = gaussian,
  chains = 4, iter = 1000, refresh = 0
)
model_1
```

@@

$$
Y_{ij}|\theta_i, \mu_, \beta_2,\beta_3 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3,\sigma^2) \\
\theta|\mu, \sigma_b   \sim N(\mu,\sigma_b) \\
\mu \sim N(..., ...) \\ 
\beta_2 \sim N(..., ...) \\
\beta_3 \sim N(..., ...) \\
\beta_4 \sim N(..., ...) \\
$$

@@

*White, StateColor, Day, Total test Results, State

@@

complexmod <- stan_glmer(
  ChinaVirusInterest ~ Day + StateColor + percent_white + totalTestResults + (Day | State), 
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

@@

@@

# Density plots
mcmc_dens_overlay(complexmod)
```

@@

>>>>

```{r}
set.seed(454)
model_1 <- stan_glm(
  ChinaVirusInterest ~ Day + percent_white+StateColor+positive,
  data = model_data, family = gaussian,
  chains = 4, iter = 10000, refresh = 0
)
model_1

@@

#### FIX 
$$
Y_{ij}|\theta_i, \mu_, \beta_2,\beta_3 \overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3,\sigma^2) \\
\theta|\mu, \sigma_b   \sim N(\mu,\sigma_b) \\
\mu \sim N(..., ...) \\ 
\beta_2 \sim N(..., ...) \\
\beta_3 \sim N(..., ...) \\
\beta_4 \sim N(..., ...) \\
$$

@@

*White, StateColor, Day, Total Test Results, State

$$
\begin{split}
Y_{ij} | b_0, b_1, \beta_0, \beta_1, \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N(b_{0i} + b_{1i} X_{ij}, \; \sigma_w^2) \\
b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\
b_{1i} | \beta_1, \sigma_{1b} & \stackrel{ind}{\sim} N(\beta_1, \sigma_{1b}^2) \\
\beta_0 & \sim N(..., ...) \\
\beta_1 & \sim N(..., ...) \\
\sigma_w & \sim Exp(...) \\
\sigma_{0b} & \sim Exp(...) \\
\sigma_{1b} & \sim Exp(...) \\
\end{split}
$$

@@

complexmod <- stan_glmer(
  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (Day | State), 
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

@@

### Feddy model eval (model 1)

###Will model eval (model 2)

@@

# Density plots
mcmc_dens_overlay(complexmod)
```
The trace and

@@

###Complex Model 
```{r}
set.seed(454)
pred_complex <- posterior_predict(
  complexmodel,
  newdata = Finaldata, transform = TRUE)

prediction_summary(y = model_data$ChinaVirusInterest,
  yrep = pred_13)
```
